---
title: "penguin"
author: "Yirui Zhang"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
install.packages(onewaytests)
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```
 our questions:
 is there a significant difference in mean flipper length for female penguins by species (chinstrap, gentoo, and adelie?)
 
 2. do some exploring
 
 new function: with+table for easy counting over multiple factors.
 update the species usung case_when
 

```{r}
counts <- with(penguins, table( species, sex))

penguins2<- penguins %>% 
  mutate(common_name =  
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gento",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )
         ) %>% 
  select(-species) %>% 
  filter(sex =="FEMALE")
```
```{r}
hist <- ggplot(penguins2, aes(c = flipper_length))+
  geom_histogram(aes(fill = common_name))+
  facet_wrap(~common_name)
hist

#QQ plot  




# Levene's test for equal variances (?2 groups.. if you have two groups, use the F-test for equal variances)
#we will use the function levenetest from the car package

#H0: variance is equal
#HA: variance is not equal
penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene

#we will retains the null ypothesis of equal variances(p = 0.06)

#group_by  summarize
variance <-penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )
variance

```
 
 #3. one-way ANOVA
 single factor: common_name (species)
 number of levels in the factor: 3 (c, g, a)
 randam variable: flipper_length(mm)
 
 is there a significant difference in mean flipper length for female C G and A penguins?
 
```{r}
#H0: mean filpper lengths across all species are equal
#HA: at least two means differ significantly
penguin_aov <-aov(flipper_length ~ common_name, data = penguins2)
summary(penguin_aov)
#At least two sample were taken from the populations with different means.

#Which one is different? all three different from each other?
#post_hoc testing using Tukey's HSD
penguin_ph <- TukeyHSD(penguin_aov)
penguin_ph

#mean ....are all significantly different from each other.
```

Mean flipper lengths for A G C are significantly different(F(df)= .., p <0.001, $\alpha\ = 0.05)$ with post-hoc TUkey's HSD $\alpha\ = 0.05$.

